---
title: "USZ_multiThreshold-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{USZ_multiThreshold--vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**USZ_multiThreshold** 

USZ_multiThreshold is an R package to extract and merge data created with the 
USZ supra-threshold test (STT) for peripheral hearing thresholds (threshold), 
temporal compresion (TC) and frequency selectivity (FS). It contains a function 
to read in a list of xls(x) files; transposing, cleaning and merging them into 
one single data frame. 

**Installation**

To install the package from github, devtools is needed. 

```{r}
devtools::install_github("pianeu/USZ_multiThreshold", subdir="auddata")
```

**Usage**

Load the package: 

```{r}
library(auddata)
```

Load your dataset: 

```{r}
file_list <- list.files(path = "/home/neuschwanderp/Desktop/Docs/R/gitHub/USZ_
                        multiThreshold/auddata/ex_data/", full.names = TRUE, 
                        recursive = TRUE)

##Call extract_thresholddata function

threshold_data <- extract_thresholddata(file_list)

head(threshold_data)


